---
title: "Kasser_Ryan_1993"
author: "Leopold Roth"
date: "2023-11-24"
output: html_document
---

# Packages
```{r}
library(dplyr)
library(readr)
library(readxl)
```

# Load Data
```{r}

#N initial:
```

# Check data
## exclude incomplete cases
```{r}

#N complete:
```

## exclude by conduction time (3SD faster than average)
```{r}

#N after time exclusion:
```

## exclude by missed attention checks (3 attention checks)
```{r}

#N after attention exclusion (final N):
```

# Clean data
## exclude columns of attention checks
```{r}

```

## exclude non-needed columns
```{r}

```

## rename variables
```{r}

```

#Descriptives
## compute reliabilities
```{r}

```

## demographics
```{r}
#describe age:

#describe best identified gender:

```

## compute means
```{r}

```

## describe distribution of means
```{r}

```

## intercorrelations of means
```{r}

```

# Analysis Kasser & Ryan (1993)
## Preliminary analysis
```{r}
#MANOVA: all aspiration importances by sex (4)
#ChatGPT example:
#manova_result <- manova(cbind(var1, var2, var3, var4) ~ sex, data = data)
#summary(manova_result)
#MANOVA: all aspiration chances by sex (4)
#follow-up t-tests by gender
#exclude non-binary??

#interaction: DV (self-act. or vitality) ~ gender + overall_asp (importance or chances) + aspiration_domain*gender
#16 interactions:
#self_act_mean ~ overall_asp_importance + importance_acceptance*gender (example)

#intercorrelate all importance (put in one)
#intercorrelate all chances
```

## Primary analysis
### hierarchical regressions
```{r}
#m1<-vitality_mean ~ overall_asp_importance
#m2<-vitality_mean ~ overall_asp_importance + importance_acceptance + importance_affiliation + importance_community + #importance_finance (see betas Table 2)

#m1<-self_act_mean ~ overall_asp_importance
#m2<-self_act_mean ~ overall_asp_importance + importance_acceptance + importance_affiliation + importance_community + #importance_finance

#zero-order correlations importances with outcomes (vitality or self_actualization)
```

### group comparisons (assessment of relative centrality)
```{r}
#z-standardize raw scores of all eight means (importances and chances)
#form dichotomized variables: e.g. 1 if financial importance is higher than community, otherwise 0
## FSI vs SAI
## FSI vs AFI
## FSI vs CFI
## FSC vs SAC
## FSC vs AFC
## FSC vs CFC
```

### guiding principles
```{r}
#average position across three sets for each guiding principle
#assess five guiding principles but only consider three
#correlate with measures (e.g. self_actualization)

#centrality analysis (through z-standardization again)
#t-tests
```





