---
title: "Kasser_Ryan_1993"
author: "Leopold Roth"
date: "2023-11-24"
output: html_document
---

# Packages
```{r}
# R version: 4.3.1
library(dplyr) # 1.1.2
library(readr) # 2.1.4
library(readxl) # 1.4.2
library(haven) # 2.5.2
library(misty) # 0.5.4
library(tidyr) # 1.3.0
library(ggplot2) # 3.4.2
library(sjPlot) # 2.8.15
library(broom) # 1.0.5
```

# Load Data
```{r}
df <- read_sav("data/[PCIRR] Kasser and Ryan (1993) replication CR_1993 [Team Leo]_NOCHECKS_December 14, 2023_07.52.sav")
df <- as.data.frame(df)
#N initial:
```

# Check data
## exclude incomplete cases
```{r}
df<-subset(df, as.numeric(Progress) == 100)
#N complete:
```

## exclude by conduction time (3SD faster than average)
```{r}
df$Duration__in_seconds_<-as.numeric(df$Duration__in_seconds_)
sd_duration<-(sd(df$Duration__in_seconds_)*3) #compute 3 times SD of duration
mean_duration<-mean(df$Duration__in_seconds_) #compute mean duration
cut_duration<-mean_duration-sd_duration #minimum time cut-off = mean time - three SD
df<-subset(df,df$Duration__in_seconds_>=cut_duration) #filter out cases with shorter usage
#N after time exclusion:
```

## exclude by missed attention checks (3 attention checks)
```{r}
df<-subset(df, AT_1 == 5)
df<-subset(df, AT_2 == 1)
df<-subset(df, AT_3 == 3)

#N after attention exclusion (final N):
```

# Clean data
## exclude columns of attention checks
```{r}
df <- df %>% select(-c("AT_1", "AT_2", "AT_3"))

```

## TODOexclude non-needed columns
```{r}

```
## recode variables
```{r}
#self-actualization
df <- df %>%
  mutate(across(grep("^SA_.*_R$", names(df), value = TRUE), ~case_when(
    . == 1 ~ 4,
    . == 2 ~ 3,
    . == 3 ~ 2,
    . == 4 ~ 1,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#vitality
df <- df %>%
  mutate(across(grep("^VI_.*_R$", names(df), value = TRUE), ~case_when(
    . == 1 ~ 7,
    . == 2 ~ 6,
    . == 3 ~ 5,
    . == 4 ~ 4,
    . == 5 ~ 3,
    . == 6 ~ 2,
    . == 7 ~ 1,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#depressive symptoms
df <- df %>%
  mutate(across(grep("CES_.*_R$", names(df), value = TRUE), ~case_when(
    . == 0 ~ 3,
    . == 1 ~ 2,
    . == 2 ~ 1,
    . == 3 ~ 0,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#trait anxiety
df <- df %>%
  mutate(across(grep("AN_.*_R$", names(df), value = TRUE), ~case_when(
    . == 4 ~ 1,
    . == 3 ~ 2,
    . == 2 ~ 3,
    . == 1 ~ 4,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))
```


## rename variables (remove _R from recode variables)
```{r}
#self-actualization
names(df) <- ifelse(grepl("^SA_", names(df)), gsub("_R$", "", names(df)), names(df))
#vitality
names(df) <- ifelse(grepl("^VI_", names(df)), gsub("_R$", "", names(df)), names(df))
#depressive symptoms
names(df) <- ifelse(grepl("^CES_", names(df)), gsub("_R$", "", names(df)), names(df))
#trait anxiety
names(df) <- ifelse(grepl("^AN_", names(df)), gsub("_R$", "", names(df)), names(df))


```

#Descriptives
## compute reliabilities
```{r}
###independent variables
#Aspiration index: importance
psych::alpha(df%>% select(starts_with("ASP_SAI")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_AFI")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_CFI")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_FSI")))[[1]]

#Aspiration index: chances
psych::alpha(df%>% select(starts_with("ASP_SAC")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_AFC")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_CFC")))[[1]]
psych::alpha(df%>% select(starts_with("ASP_FSC")))[[1]]

#Guiding principles:
## money
psych::alpha(df%>%select(grep("^GPR_.*_1$", names(df), value = TRUE)))[[1]]
##family security
psych::alpha(df%>%select(grep("^GPR_.*_2$", names(df), value = TRUE)))[[1]]
##global welfare
psych::alpha(df%>%select(grep("^GPR_.*_3$", names(df), value = TRUE)))[[1]]
##spirituality
psych::alpha(df%>%select(grep("^GPR_.*_4$", names(df), value = TRUE)))[[1]]
##hedonism
psych::alpha(df%>%select(grep("^GPR_.*_5$", names(df), value = TRUE)))[[1]]

###dependent variables
#self-actualization
psych::alpha(df%>% select(starts_with("SA_")))[[1]]
#vitality
psych::alpha(df%>% select(starts_with("VI_")))[[1]]
#control orientation (only care about control-subscale)
psych::alpha(df%>%select(grep("^CO_.*_C$", names(df), value = TRUE)))[[1]]
#depressive symptoms
psych::alpha(df%>% select(starts_with("CES_")))[[1]]
#trait anxiety
psych::alpha(df%>% select(starts_with("AN_")))[[1]]
```

## demographics
```{r}
#describe age:
psych::describe(df$age)

#describe best identified gender:
table(df$gender) #1 = male, 2 = female, 3 = other, 4 = rather not disclose
```

## compute means
```{r}
###independent variables
#aspiration index: importances
df <- df %>% mutate(mean_asp_asi = rowMeans(select(., starts_with("ASP_SAI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_afi = rowMeans(select(., starts_with("ASP_AFI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_cfi = rowMeans(select(., starts_with("ASP_CFI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_fsi = rowMeans(select(., starts_with("ASP_FSI")), na.rm = TRUE))

#aspiration index: overall importance
df <- df %>%
  mutate(mean_asp_overall_importance = rowMeans(select(.,starts_with("ASP_SAI"),
                                                         starts_with("ASP_AFI"),
                                                         starts_with("ASP_CFI"),
                                                         starts_with("ASP_FSI")), 
                                                        na.rm = TRUE))
#aspiration index: chances
df <- df %>% mutate(mean_asp_asc = rowMeans(select(., starts_with("ASP_SAC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_afc = rowMeans(select(., starts_with("ASP_AFC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_cfc = rowMeans(select(., starts_with("ASP_CFC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_fsc = rowMeans(select(., starts_with("ASP_FSC")), na.rm = TRUE))

#aspiration index: overall chances
df <- df %>%
  mutate(mean_asp_overall_chances = rowMeans(select(.,starts_with("ASP_SAC"),
                                                         starts_with("ASP_AFC"),
                                                         starts_with("ASP_CFC"),
                                                         starts_with("ASP_FSC")), 
                                                        na.rm = TRUE))

#guiding principles: mean position in rank-ordering across three rankings
#money
df <- df %>% mutate(mean_gpr_money = 
                      rowMeans(select(., grep("^GPR_.*_1$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#family security
df <- df %>% mutate(mean_gpr_family_security = 
                      rowMeans(select(., grep("^GPR_.*_2$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#global welfare
df <- df %>% mutate(mean_gpr_global_welfare = 
                      rowMeans(select(., grep("^GPR_.*_3$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#spirituality
df <- df %>% mutate(mean_gpr_spirituality = 
                      rowMeans(select(., grep("^GPR_.*_4$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#hedonism
df <- df %>% mutate(mean_gpr_hedonism = 
                      rowMeans(select(., grep("^GPR_.*_5$", names(df), value = TRUE)), 
                      na.rm = TRUE))

###dependent variables
#self-actualization
df <- df %>% mutate(mean_self_actualization = 
                      rowMeans(select(., starts_with("SA_")), na.rm = TRUE))
#vitality
df <- df %>% mutate(mean_vitality = 
                      rowMeans(select(., starts_with("VI_")), na.rm = TRUE))
#control orientation
df <- df %>% mutate(mean_control_orientation = 
                      rowMeans(select(., grep("^CO_.*_C$", names(df), value = TRUE)), 
                      na.rm = TRUE))

#depressive symptoms
df <- df %>% mutate(mean_depressive_symptoms = 
                      rowMeans(select(., starts_with("CES_")), na.rm = TRUE))

#trait anxiety
df <- df %>% mutate(mean_trait_anxiety = 
                      rowMeans(select(., starts_with("AN_")), na.rm = TRUE))
```

## describe distribution of means
```{r}
#numerically describe all means
df_means <- df %>% select (starts_with("mean"))
df_means_describe <- psych::describe(df_means) #save descriptives in extra df

#plot all means
long_df_means <- pivot_longer(df_means, cols = everything(), names_to = "variable", values_to = "value")

ggplot(long_df_means, aes(x = value)) +
  geom_histogram(bins = 30, fill = "blue", color = "black") +
  facet_wrap(~ variable, scales = "free_x") +
  theme_minimal() +
  labs(title = "Histograms of All Columns", x = "Value", y = "Frequency")

```

## intercorrelations of means
```{r}
df_means %>%
  correlation::correlation()
```

# Analysis Kasser & Ryan (1993)
## Preliminary analysis
### MANOVA by gender with follow up t-tests
```{r}
#exclude individuals which didn't indicate to identify as female/male
df_manova <- subset(df, gender < 3) 

#manova importances
manova_importances <- manova(cbind(mean_asp_asi,mean_asp_afi,mean_asp_cfi,mean_asp_fsi)
                             ~ gender, data = df_manova)
summary(manova_importances)
report::report(manova_importances)

#follow up t-tests
report::report(t.test(mean_asp_asi ~gender, data = df_manova))
report::report(t.test(mean_asp_afi ~gender, data = df_manova))
report::report(t.test(mean_asp_cfi ~gender, data = df_manova))
report::report(t.test(mean_asp_fsi ~gender, data = df_manova))

#manova chances
manova_chances <- manova(cbind(mean_asp_asc,mean_asp_afc,mean_asp_cfc,mean_asp_fsc)
                             ~ gender, data = df_manova)
summary(manova_chances)
report::report(manova_chances)

#follow up t-tests
report::report(t.test(mean_asp_asc ~gender, data = df_manova))
report::report(t.test(mean_asp_afc ~gender, data = df_manova))
report::report(t.test(mean_asp_cfc ~gender, data = df_manova))
report::report(t.test(mean_asp_fsc ~gender, data = df_manova))

#interaction: DV (self-act. or vitality) ~ gender + overall_asp (importance or chances) + aspiration_domain*gender
#16 interactions:
#self_act_mean ~ overall_asp_importance + importance_acceptance*gender (example)

#intercorrelate all importance (put in one)
#intercorrelate all chances
```

### outcome by gender and aspiration interactions
```{r}
extract_full_name <- function(string) {
    parts <- unlist(strsplit(string, "_"))
    # Assuming the dependent variable name is the first three parts of the split
    full_name <- paste(parts[1:3], collapse = "_")
    return(full_name)
}

run_models <- function(dependent_var, data) {
  models <- list()
  interactions_i <- c("mean_asp_asi", "mean_asp_afi", "mean_asp_cfi", "mean_asp_fsi")
  interactions_c <- c("mean_asp_asc", "mean_asp_afc", "mean_asp_cfc", "mean_asp_fsc")
  
  # Pair overall_importance with interactions ending in 'i'
  for (inter in interactions_i) {
    model_formula <- as.formula(paste(dependent_var, "~ mean_asp_overall_importance +", inter, "*gender"))
    model_name <- paste(dependent_var, "mean_asp_overall_importance", inter, sep="_")
    models[[model_name]] <- lm(model_formula, data = data)
  }

  # Pair overall_chances with interactions ending in 'c'
  for (inter in interactions_c) {
    model_formula <- as.formula(paste(dependent_var, "~ mean_asp_overall_chances +", inter, "*gender"))
    model_name <- paste(dependent_var, "mean_asp_overall_chances", inter, sep="_")
    models[[model_name]] <- lm(model_formula, data = data)
  }
  
  return(models)
}

dependent_vars <- c("mean_self_actualization","mean_vitality","mean_control_orientation", "mean_depressive_symptoms", "mean_trait_anxiety")
all_models <- list()

for (var in dependent_vars) {
  all_models[[var]] <- run_models(var, df)
}

model_summaries <- list()

for (var in names(all_models)) {
  model_summaries[[var]] <- lapply(all_models[[var]], broom::tidy)
}

results_df <- data.frame()

for (var in names(all_models)) {
    for (model_name in names(all_models[[var]])) {
        model_summary <- broom::tidy(all_models[[var]][[model_name]])
        model_summary$model <- model_name  # Add the model name directly here
        results_df <- rbind(results_df, model_summary)
    }
}

filtered_df <- results_df[grepl(":gender", results_df$term), ]

filtered_df$model <- sapply(filtered_df$model, extract_full_name)

df_results_gender_interactions <- filtered_df

#find significant interactions
df_results_gender_interactions <- subset(df_results_gender_interactions, p.value < .05)
```


## Primary analysis
### hierarchical regressions
```{r}
#m1<-vitality_mean ~ overall_asp_importance
#m2<-vitality_mean ~ overall_asp_importance + importance_acceptance + importance_affiliation + importance_community + #importance_finance (see betas Table 2)

#m1<-self_act_mean ~ overall_asp_importance
#m2<-self_act_mean ~ overall_asp_importance + importance_acceptance + importance_affiliation + importance_community + #importance_finance

#zero-order correlations importances with outcomes (vitality or self_actualization)
```

### group comparisons (assessment of relative centrality)
```{r}
#z-standardize raw scores of all eight means (importances and chances)
#form dichotomized variables: e.g. 1 if financial importance is higher than community, otherwise 0
## FSI vs SAI
## FSI vs AFI
## FSI vs CFI
## FSC vs SAC
## FSC vs AFC
## FSC vs CFC
```

### guiding principles
```{r}
#average position across three sets for each guiding principle
#assess five guiding principles but only consider three
#correlate with measures (e.g. self_actualization)

#centrality analysis (through z-standardization again)
#t-tests
```





