---
title: "Kasser_Ryan_New"
author: "Leopold Roth"
date: "2024-10-23"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

# Packages
```{r}
# R version: 4.3.1
library(dplyr) # 1.1.2
library(readr) # 2.1.4
library(readxl) # 1.4.2
library(haven) # 2.5.2
library(misty) # 0.5.4
library(tidyr) # 1.3.0
library(ggplot2) # 3.4.4
library(sjPlot) # 2.8.14
library(broom) # 1.0.5
library(writexl)
library(forcats)
library(ggpubr)
```

# Load Data
```{r}
#this chunk loads the dataset, strores it in the object 'df' and reassures that it is a dataframe
df <- read_sav("data/[PCIRR] Kasser and Ryan (1993) replication CR_1993 [Team Leo]_NOCHECKS_December 14, 2023_07.52.sav")
df <- as.data.frame(df)
#N initial:
```

# Check data
## exclude incomplete cases
```{r}
#this subsets the data to only keep cases who completed the entire survey
df<-subset(df, as.numeric(Progress) == 100)
#N complete:
```

## exclude by conduction time (3SD faster than average)
```{r}
#this serves the purpose to exclude cases in which people/bots clicked through everything as fast as possible
df$Duration__in_seconds_<-as.numeric(df$Duration__in_seconds_)
sd_duration<-(sd(df$Duration__in_seconds_)*3) #compute 3 times SD of duration
mean_duration<-mean(df$Duration__in_seconds_) #compute mean duration
cut_duration<-mean_duration-sd_duration #minimum time cut-off = mean time - three SD
df<-subset(df,df$Duration__in_seconds_>=cut_duration) #filter out cases with shorter usage
#N after time exclusion:
```

## exclude by missed attention checks (3 attention checks) (deactivated in simulation)
```{r}
#the survey included 3 attention checks; incorrectly responding to one of these will lead to exclusion from the final dataset
#df<-subset(df, AT_1 == 5)
#df<-subset(df, AT_2 == 1)
#df<-subset(df, AT_3 == 3)

#N after attention exclusion (final N):
```

# Clean data
## exclude columns of attention checks
```{r}
#after the exclusion, we exclude the attention check columns from the dataset
df <- df %>% select(-c("AT_1", "AT_2", "AT_3"))
```

## TODOexclude non-needed columns
```{r}
#this will be updated, in case qualtrics attaches columns, which are not needed for the analysis
```
## recode variables
```{r}
#this chunk recodes variables which were reverse coded. These were marked with _R in the variable name
#as the different scales operate on different scale widths, we need to select the reversed items by scale, using the starting letters or the variables (e.g., SA for the self-actualization items)
#the code then 'takes' all variables, starting with 'SA' and ending with '_R' and recodes them, based on the specific scale (1 to 4 or 1 to 7 etc.)
#self-actualization
df <- df %>%
  mutate(across(grep("^SA_.*_R$", names(df), value = TRUE), ~case_when(
    . == 1 ~ 4,
    . == 2 ~ 3,
    . == 3 ~ 2,
    . == 4 ~ 1,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#vitality
df <- df %>%
  mutate(across(grep("^VI_.*_R$", names(df), value = TRUE), ~case_when(
    . == 1 ~ 7,
    . == 2 ~ 6,
    . == 3 ~ 5,
    . == 4 ~ 4,
    . == 5 ~ 3,
    . == 6 ~ 2,
    . == 7 ~ 1,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#depressive symptoms
df <- df %>%
  mutate(across(grep("CES_.*_R$", names(df), value = TRUE), ~case_when(
    . == 0 ~ 3,
    . == 1 ~ 2,
    . == 2 ~ 1,
    . == 3 ~ 0,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))

#trait anxiety
df <- df %>%
  mutate(across(grep("AN_.*_R$", names(df), value = TRUE), ~case_when(
    . == 4 ~ 1,
    . == 3 ~ 2,
    . == 2 ~ 3,
    . == 1 ~ 4,
    TRUE ~ . # keeps original value if none of the above conditions are met
  )))
```


## rename variables (remove _R from recode variables)
```{r}
#after recoding the variables (see chunk above), the marking of the reversed variables is no longer needed
#hence, the '_R' is removed from the variables names

#self-actualization
names(df) <- ifelse(grepl("^SA_", names(df)), gsub("_R$", "", names(df)), names(df))
#vitality
names(df) <- ifelse(grepl("^VI_", names(df)), gsub("_R$", "", names(df)), names(df))
#depressive symptoms
names(df) <- ifelse(grepl("^CES_", names(df)), gsub("_R$", "", names(df)), names(df))
#trait anxiety
names(df) <- ifelse(grepl("^AN_", names(df)), gsub("_R$", "", names(df)), names(df))


```

# Descriptives
## compute reliabilities
```{r}
#this chunk computes the reliabilities (cronbachs alpha) for all measures of interest in the study. By keeping the [[1]] in every line, only the alpha is reported
#to get more details on the item level, delete the [[1]]

###independent variables
#Aspiration index: importance
alpha_1 <- psych::alpha(df%>% select(starts_with("ASP_SAI")))[[1]]
alpha_2 <- psych::alpha(df%>% select(starts_with("ASP_AFI")))[[1]]
alpha_3 <- psych::alpha(df%>% select(starts_with("ASP_CFI")))[[1]]
alpha_4 <- psych::alpha(df%>% select(starts_with("ASP_FSI")))[[1]]

#Aspiration index: chances
alpha_5 <- psych::alpha(df%>% select(starts_with("ASP_SAC")))[[1]]
alpha_6 <- psych::alpha(df%>% select(starts_with("ASP_AFC")))[[1]]
alpha_7 <- psych::alpha(df%>% select(starts_with("ASP_CFC")))[[1]]
alpha_8 <- psych::alpha(df%>% select(starts_with("ASP_FSC")))[[1]]

#Guiding principles:
## money
alpha_9 <- psych::alpha(df%>%select(grep("^GPR_.*_1$", names(df), value = TRUE)))[[1]]
##family security
alpha_10 <- psych::alpha(df%>%select(grep("^GPR_.*_2$", names(df), value = TRUE)))[[1]]
##global welfare
alpha_11 <- psych::alpha(df%>%select(grep("^GPR_.*_3$", names(df), value = TRUE)))[[1]]
##spirituality
psych::alpha(df%>%select(grep("^GPR_.*_4$", names(df), value = TRUE)))[[1]]
##hedonism
psych::alpha(df%>%select(grep("^GPR_.*_5$", names(df), value = TRUE)))[[1]]

###dependent variables
#self-actualization
alpha_12 <- psych::alpha(df%>% select(starts_with("SA_")))[[1]]
#vitality
alpha_13 <- psych::alpha(df%>% select(starts_with("VI_")))[[1]]
#control orientation (only care about control-subscale)
alpha_14 <- psych::alpha(df%>%select(grep("^CO_.*_C$", names(df), value = TRUE)))[[1]]
#depressive symptoms
alpha_15 <- psych::alpha(df%>% select(starts_with("CES_")))[[1]]
#trait anxiety
alpha_16 <- psych::alpha(df%>% select(starts_with("AN_")))[[1]]

#save all needed reliabilties for reporting (this computes means and SD already)
reliabilities <- rbind(alpha_1, alpha_2, alpha_3, alpha_4,
                       alpha_5, alpha_6, alpha_7, alpha_8,
                       alpha_9, alpha_10, alpha_11, alpha_12,
                       alpha_13, alpha_14, alpha_15, alpha_16)

reliabilities$labels <- c("SAI", "AFI", "CFI", "FSI", "SAC", "AFC", "CFC", "FSC",
                          "gpr_money", "gpr_family", "gpr_welfare", "self_actualization",
                          "vitality", "control_orientation", "depressive_symptoms", "trait_anxiety")

#reduce to needed columns I
reliabilities <- reliabilities %>%
  select(c(labels, mean, sd, raw_alpha))

#round numeric values
reliabilities <- data.frame(lapply(reliabilities, function(x) if(is.numeric(x)) round(x, 2) else x))

#compute combined M (SD) column
reliabilities$M_SD <- paste(reliabilities$mean, " (", reliabilities$sd, ")", sep="")

#reduce to needed columns II
reliabilities <- reliabilities %>%
  select(c(labels, M_SD, raw_alpha))

#save relevant data and copy-paste to document (replace ',' with '.' in reliabilties and change e.g. 0.30 to .30)
write_xlsx(reliabilities[, c("M_SD", "raw_alpha")], "M_SD_rel_data.xlsx")

#exclude non-needed df
rm(list = c("alpha_1", "alpha_2", "alpha_3", "alpha_4",
            "alpha_5", "alpha_6", "alpha_7", "alpha_8",
            "alpha_9", "alpha_10", "alpha_11", "alpha_12",
            "alpha_13", "alpha_14", "alpha_15", "alpha_16"))
```

## demographics
```{r}
###describe age:
psych::describe(df$age)
ggplot(df,aes(y = age))+
  geom_boxplot()+
  theme_classic()

###describe best identified gender:
table(df$gender) #1 = male, 2 = female, 3 = other, 4 = rather not disclose


# Calculate the table and convert it to a data frame
gender_table <- table(df$gender)
gender_df <- data.frame(Category = names(gender_table), Count = as.integer(gender_table))

# Add a column for percentages
gender_df$Percentage <- (gender_df$Count / sum(gender_df$Count)) * 100

# Update Category names to be more descriptive
gender_df$Category <- factor(gender_df$Category, levels = c("1", "2", "3", "4"),
                             labels = c("Male", "Female", "Other", "Rather not disclose"))

# Plot
ggplot(gender_df, aes(x = Category, y = Percentage, fill = Category)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Pastel1") + 
  labs(title = "Gender Distribution", x = "Gender", y = "Percentage (%)") +
  theme_classic() +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), vjust = -0.5)

```

## compute means
```{r}
#this chunk computes all needed means for the analysis
#first all independent variables, afterwards the dependent variables

###independent variables
#aspiration index: importances
df <- df %>% mutate(mean_asp_sai = rowMeans(select(., starts_with("ASP_SAI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_afi = rowMeans(select(., starts_with("ASP_AFI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_cfi = rowMeans(select(., starts_with("ASP_CFI")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_fsi = rowMeans(select(., starts_with("ASP_FSI")), na.rm = TRUE))

#aspiration index: overall importance
df <- df %>%
  mutate(mean_asp_overall_importance = rowMeans(select(.,starts_with("ASP_SAI"),
                                                         starts_with("ASP_AFI"),
                                                         starts_with("ASP_CFI"),
                                                         starts_with("ASP_FSI")), 
                                                        na.rm = TRUE))
#aspiration index: chances
df <- df %>% mutate(mean_asp_sac = rowMeans(select(., starts_with("ASP_SAC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_afc = rowMeans(select(., starts_with("ASP_AFC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_cfc = rowMeans(select(., starts_with("ASP_CFC")), na.rm = TRUE))
df <- df %>% mutate(mean_asp_fsc = rowMeans(select(., starts_with("ASP_FSC")), na.rm = TRUE))

#aspiration index: overall chances
df <- df %>%
  mutate(mean_asp_overall_chances = rowMeans(select(.,starts_with("ASP_SAC"),
                                                         starts_with("ASP_AFC"),
                                                         starts_with("ASP_CFC"),
                                                         starts_with("ASP_FSC")), 
                                                        na.rm = TRUE))

#guiding principles: mean position in rank-ordering across three rankings
#money
df <- df %>% mutate(mean_gpr_money = 
                      rowMeans(select(., grep("^GPR_.*_1$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#family security
df <- df %>% mutate(mean_gpr_family_security = 
                      rowMeans(select(., grep("^GPR_.*_2$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#global welfare
df <- df %>% mutate(mean_gpr_global_welfare = 
                      rowMeans(select(., grep("^GPR_.*_3$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#spirituality
df <- df %>% mutate(mean_gpr_spirituality = 
                      rowMeans(select(., grep("^GPR_.*_4$", names(df), value = TRUE)), 
                      na.rm = TRUE))
#hedonism
df <- df %>% mutate(mean_gpr_hedonism = 
                      rowMeans(select(., grep("^GPR_.*_5$", names(df), value = TRUE)), 
                      na.rm = TRUE))

###dependent variables
#self-actualization
df <- df %>% mutate(mean_self_actualization = 
                      rowMeans(select(., starts_with("SA_")), na.rm = TRUE))
#vitality
df <- df %>% mutate(mean_vitality = 
                      rowMeans(select(., starts_with("VI_")), na.rm = TRUE))
#control orientation
df <- df %>% mutate(mean_control_orientation = 
                      rowMeans(select(., grep("^CO_.*_C$", names(df), value = TRUE)), 
                      na.rm = TRUE))

#depressive symptoms
df <- df %>% mutate(mean_depressive_symptoms = 
                      rowMeans(select(., starts_with("CES_")), na.rm = TRUE))

#trait anxiety
df <- df %>% mutate(mean_trait_anxiety = 
                      rowMeans(select(., starts_with("AN_")), na.rm = TRUE))
```

## describe distribution of means
```{r}
#here we receive all relevant descriptive informations about the distribution properties of the means
#numerically describe all means
df_means <- df %>% select (starts_with("mean"))
df_means_describe <- psych::describe(df_means) #save descriptives in extra df: this contains detailed informations about all means (e.g., case number, Sd etc.)

#plot all means
long_df_means <- pivot_longer(df_means, cols = everything(), names_to = "variable", values_to = "value")

ggplot(long_df_means, aes(x = value)) +
  geom_histogram(bins = 30, fill = "blue", color = "black") +
  facet_wrap(~ variable, scales = "free_x") +
  theme_minimal() +
  labs(title = "Histograms of All Means", x = "Value", y = "Frequency")

```

## intercorrelations of means
```{r}
#here we create a correlation table between all means
df_means %>%
  correlation::correlation(p_adjust = "none")%>% #this disables any alpha corrections, but can be replace with other methods (https://rdrr.io/github/easystats/correlation/man/correlation.html)
  summary(redundant = TRUE) %>%
  plot()

df_means %>%
  correlation::correlation(p_adjust = "none")%>%
  filter(p < .05) #this is a subset with significant correlations at .05

df_means %>%
  correlation::correlation(p_adjust = "none")%>%
  filter(p < .001) #this is a subset with significant correlations at .001
  
```

# Target Analaysis
## correlations {.tabset}
### importance
```{r}
## self-actualization
df_means %>%
  select(mean_asp_fsi, mean_self_actualization) %>%
  correlation::correlation() %>%
  print()

## vitality
df_means %>%
  select(mean_asp_fsi, mean_vitality) %>%
  correlation::correlation() %>%
  print()

## control orientation
df_means %>%
  select(mean_asp_fsi, mean_control_orientation) %>%
  correlation::correlation() %>%
  print()

## depressive symptoms
df_means %>%
  select(mean_asp_fsi, mean_depressive_symptoms) %>%
  correlation::correlation() %>%
  print()

## anxiety
df_means %>%
  select(mean_asp_fsi, mean_trait_anxiety) %>%
  correlation::correlation() %>%
  print()
```

### chances
```{r}
## self-actualization
df_means %>%
  select(mean_asp_fsc, mean_self_actualization) %>%
  correlation::correlation() %>%
  print()

## vitality
df_means %>%
  select(mean_asp_fsc, mean_vitality) %>%
  correlation::correlation() %>%
  print()

## control orientation
df_means %>%
  select(mean_asp_fsc, mean_control_orientation) %>%
  correlation::correlation() %>%
  print()

## depressive symptoms
df_means %>%
  select(mean_asp_fsc, mean_depressive_symptoms) %>%
  correlation::correlation() %>%
  print()

## anxiety
df_means %>%
  select(mean_asp_fsc, mean_trait_anxiety) %>%
  correlation::correlation() %>%
  print()
```

### rank
```{r}
## self-actualization
df_means %>%
  select(mean_gpr_money, mean_self_actualization) %>%
  correlation::correlation() %>%
  print()

## vitality
df_means %>%
  select(mean_gpr_money, mean_vitality) %>%
  correlation::correlation() %>%
  print()

## control orientation
df_means %>%
  select(mean_gpr_money, mean_control_orientation) %>%
  correlation::correlation() %>%
  print()

## depressive symptoms
df_means %>%
  select(mean_gpr_money, mean_depressive_symptoms) %>%
  correlation::correlation() %>%
  print()

## anxiety
df_means %>%
  select(mean_gpr_money, mean_trait_anxiety) %>%
  correlation::correlation() %>%
  print()
```

## regressions {.tabset}
### importance 
```{r}
m1 <- lm(mean_self_actualization ~ mean_asp_overall_importance +
                                      mean_asp_sai +
                                      mean_asp_afi +
                                      mean_asp_fsi +
                                      mean_asp_cfi, data = df_means)

tab_model(m1, show.std = TRUE)

m2 <- lm(mean_vitality ~ mean_asp_overall_importance +
                                      mean_asp_sai +
                                      mean_asp_afi +
                                      mean_asp_fsi +
                                      mean_asp_cfi, data = df_means)

tab_model(m2, show.std = TRUE)

m3 <- lm(mean_control_orientation ~ mean_asp_overall_importance +
                                      mean_asp_sai +
                                      mean_asp_afi +
                                      mean_asp_fsi +
                                      mean_asp_cfi, data = df_means)

tab_model(m3, show.std = TRUE)

m4 <- lm(mean_depressive_symptoms ~ mean_asp_overall_importance +
                                      mean_asp_sai +
                                      mean_asp_afi +
                                      mean_asp_fsi +
                                      mean_asp_cfi, data = df_means)

tab_model(m4, show.std = TRUE)

m5 <- lm(mean_trait_anxiety ~ mean_asp_overall_importance +
                                      mean_asp_sai +
                                      mean_asp_afi +
                                      mean_asp_fsi +
                                      mean_asp_cfi, data = df_means)

tab_model(m5, show.std = TRUE)
```

### chances
```{r}
m1 <- lm(mean_self_actualization ~ mean_asp_overall_chances +
                                      mean_asp_sac +
                                      mean_asp_afc +
                                      mean_asp_fsc +
                                      mean_asp_cfc, data = df_means)

tab_model(m1, show.std = TRUE)

m2 <- lm(mean_vitality ~ mean_asp_overall_chances +
                                      mean_asp_sac +
                                      mean_asp_afc +
                                      mean_asp_fsc +
                                      mean_asp_cfc, data = df_means)

tab_model(m2, show.std = TRUE)

m3 <- lm(mean_control_orientation ~ mean_asp_overall_chances +
                                      mean_asp_sac +
                                      mean_asp_afc +
                                      mean_asp_fsc +
                                      mean_asp_cfc, data = df_means)

tab_model(m3, show.std = TRUE)

m4 <- lm(mean_depressive_symptoms ~ mean_asp_overall_chances +
                                      mean_asp_sac +
                                      mean_asp_afc +
                                      mean_asp_fsc +
                                      mean_asp_cfc, data = df_means)

tab_model(m4, show.std = TRUE)

m5 <- lm(mean_trait_anxiety ~ mean_asp_overall_chances +
                                      mean_asp_sac +
                                      mean_asp_afc +
                                      mean_asp_fsc +
                                      mean_asp_cfc, data = df_means)

tab_model(m5, show.std = TRUE)
```


