---
title: "overall_effect"
author: "Dominik Meindl"
date: "2023-12-15"
output: html_document
---
# Outline 
This document will contain a simplified meta analysis for both the t-test and correlations to determine an overall effect found by either of the tests.

# Packages
```{r Package Loading, message=FALSE, warning=FALSE, include=FALSE}
#Packages----
#using base 4.3.2
library(esc) #0.5.1
library(readr) #2.1.4
library(DescTools) #0.99.52
library(metafor) #4.4-0
library(tidyverse) # 2.0.0
```

# Data Preparation
This section will prepare the raw data for use in the later analysis. If you ran the Power_Analysis.rmd then the dataset for T-tests is already accessible to you and can be skipped. For sake of completeness it has been added here as well.

## Load Data
This is raw data extracted from the publication by Kasser & Ryan (1993). Such as Means, standard deviations (SD), t values and significance (.05 or .10) as well as which study this data has been extracted from.

df = all values concerning t tests
- mx: mean of first variable
- my: mean of second variable (FSI/FSC)
- sdx: sd of first variable
- sdy: sd of second variable (FSI/FSC)
- t: t-value
- sig05: 1 if p <.05
- sig10: 1 if p <.10
- study: 1 for study 1, 2 for study 2
- n: sample size

df2 = all values concerning correlations
- beta: beta values
- correlation: Pearsons r
- sig05_beta: 1 if p <.05 (beta)
- sig05_cor: 1 if p <.05 (r)
- sig10_beta: 1 if p <.10 (beta)
- sig10_cor: 1 if p <.10 (r)
- study: 1 for study 1, 2 for study 2
- n: sample size

```{r}
#load data----
df <- read_csv2("./data/ttests_raw.csv")
df2 <- read_csv2("./data/correlations_raw.csv")
```

## Power Transformations - Cohens D Values of T-Tests
Calculate Cohens d for all t-tests using a custom function.
We will then remerge this date with the original dataframe to get one file containing all information. 
This is the same code as used in Power_Analysis.rmd.

Due to an error introduced by R 4.3.2 we had to change our approach, we now have to use custom code to extract the same data as the esc::esc_mean_sd function.

```{r}
# custom Function to calculate Cohen's d and its statistics
cohen_d_with_stats <- function(mx, my, sdx, sdy, n) {
  pooled_sd <- sqrt(((n - 1) * sdx^2 + (n - 1) * sdy^2) / (n + n - 2))
  d <- (mx - my) / pooled_sd
  var_d <- (n + n) / (n * n) + (d^2 / (2 * (n + n - 2)))
  se_d <- sqrt(var_d)
  ci_95_low <- d - 1.96 * se_d
  ci_95_high <- d + 1.96 * se_d
  return(c(d, var_d, se_d, ci_95_low, ci_95_high))
}

# Apply the function to each row
results <- apply(df, 1, function(x) cohen_d_with_stats(as.numeric(x['mx']), 
                                                       as.numeric(x['my']), 
                                                       as.numeric(x['sdx']), 
                                                       as.numeric(x['sdy']), 
                                                       as.numeric(x['n'])))

# Converting results to a dataframe
results_df <- as.data.frame(t(results))
names(results_df) <- c("es", "var", "se", "ci.lo", "ci.hi")

# Merging results with the original dataframe
cohens_d <- cbind(df, results_df)

#write.csv2(cohens_d, "./data/cohens_d_ttests.csv")
```

## Preparation of correlation data
As the correlations reported by Kasser & Ryan (1993) do not contain any confidence intervals such need to be calculated.
We use the DescTools package function CorCI which automatically calculates confidence intervals around our correlations.
For this to function we need to run the code in a for loop, as data output from this function cannot be added to a dataframe due to the format. Using a for loop circumvents that issue and gives us an interval for the variables. 

We then convert that data output into a dataframe again.

```{r}
df2 <- as.data.frame(df2)

for(i in 1:nrow(df2)){
    x <- DescTools::CorCI(df2$correlation[i], df2$n[i], conf.level = 0.95, alternative=c("two.sided"))
  if(i == 1) {
    correlations_CI <- x
  } else {
    correlations_CI <- rbind(correlations_CI, x) # Add new data to dataframe
  }
}

correlations_CI <- as.data.frame(correlations_CI)
```

We then needed to add all identifiers back into the newly generated dataframe.
Which we then save.

```{r}
correlations_CI$variable <- df2$variable
correlations_CI$study <- df2$study
correlations_CI$n <- df2$n

#write.csv2(correlations_CI, "./data/correlations_CI.csv")
```



# Overall Effect analysis
All following calculations are conducted using the metafor package.

## Load previously prepared data
```{r}
ma2 <- read.csv2("data/cohens_d_ttests.csv")
ma3 <- read.csv2("data/correlations_CI.csv")
```

## Summary effect T-test's

For final data preparation we use the abs function to turn all effects into the same (positive) direction, as to make the effects compareable.

We then add a running id to each collumn.

```{r}
#---- summary effect t tests ---- 
ma2$es <- abs(ma2$es) #using absolute to turn all effects positive
ma2$es.id <- seq.int(nrow(ma2))
```

Following this we use a Meta-Analysis via Multivariate/Multilevel Linear (Mixed-Effects) Models to calculate a model for the overall effect. Which we then look into using the summary function.

```{r}
overall.ma2<-rma.mv(yi=es,
                    V=var,
                    random=list(~1|study/es.id),
                    tdist=TRUE,
                    method="REML",
                    slab=study,
                    data=ma2)	

summary(overall.ma2)
```


## Summary effect correlation's

For final data preparation we use the abs function to turn all effects into the same (positive) direction, as to make the effects comparable.

We then add a running id to each column.

```{r}
#---- summary effect cor ----

ma3$cor <- abs(ma3$cor) #using abs to turn all results positive

ma3$es.id <- seq.int(nrow(ma3))
```

For the analysis using the correlation data we need to add a variable containing the Variance of the correlation to do this we use the escalc function of the metafor package. Which uses the correlations and sample size to determine the variance which will then be added back into the dataset.

```{r}
x <- escalc(measure="COR", ri=ma3$cor, ni=ma3$n) #calc variance of correlations
ma3$var <- x$vi
```

Following this we use a Meta-Analysis via Multivariate/Multilevel Linear (Mixed-Effects) Models to calculate a model for the overall effect. Which we then look into using the summary function.

```{r}
overall.ma3<-rma.mv(yi=cor,
                    V=var,
                    random=list(~1|study/es.id),
                    tdist=TRUE,
                    method="REML",
                    slab=study,
                    data=ma3)	

summary(overall.ma3)

```

