---
title: "Plots"
author: "Dominik Meindl"
date: "2024-01-15"
output: html_document
---
# Outline 
This document will contain the codes to produce all plots used in the reporting of this study.

# Packages
```{r}
#Packages --- using R 4.3.2
library(forester) # 0.2.0
library(tidyverse) # 2.0.0
library(dplyr) # 1.1.4
library(DescTools) # 0.99.52
#Installing Forester

#install.packages("devtools")
#library(devtools)
#devtools::install_github("rdboyes/forester")

# Load font for forester ----
#library(extrafont)

#> Registering fonts with R
#loadfonts(deANce = "win") # Font used by Forester later on, Windows only
#> Roboto Condensed already registered with windowsFonts().
#windowsFonts("Fira Sans" = windowsFont("Fira Sans"))
```

# Data Preparation
This section will prepare the raw data for use in the later analysis. Please run this code only after youve run either the "overall_effect.Rmd" or "Power_Analysis.Rmd", as this requires code requires the datasets generated bei either of these Markdown files.

## Load Data
This is  data which has been extracted from the publication by Kasser & Ryan (1993) and then be prepared. We will drop some of the collumns from the loaded data, in the end we will only have the variable name, study, estimate for D, variance, standard error, as well as the confidence intervalls for each Cohens D.

table = all values concerning t tests
- variable: variable Name 
- study: 1 for study 1, 2 for study 2
- es: cohens D effectsize
- var: variance of es
- se: standard error of es
- ci.lo: Lower bound of cofidence intervall around es
- ci.hi: Upper bound of cofidence intervall around es

df2 = all values concerning correlations
- variable: variable Name 
- beta: beta values for correlations
- correlation: cor. r value
- sig05_beta: 1 if beta is sig. with p<0.05, NA if not
- sig05_cor: 1 if cor. is sig. with p<0.05, NA if not
- sig10_beta: 1 if beta is sig. with p<0.10, NA if not
- sig10_cor: 1 if cor. is sig. with p<0.10, NA if not
- study: 1 for study 1, 2 for study 2
- n: number of participants 


```{r}
table <- read.csv2("./data/cohens_d_ttests.csv")
df2 <- read.csv2("./data/correlations_raw.csv")
```


# T-Tests data preparation (Cohens D T tests)
We will start by preparing all data used in the plots as forester requires a certain data structure.
Here we will add the lines telling us which variable and study is used.

First we start by subsetting the dataset using only the neccesary collumns.
We then sort those by the Suffixes (Suffix = Variable) and study.

```{r}
#Subsetting data and renaming variables for easier datahandling
table <- table%>%select(c("variable","study","es","var","se","ci.lo","ci.hi"))
table <- table %>%  #renaming variables
              rename(
                Variable = variable,
                Estimate = es
 )
table$header <- NA

# Sort data
suf <- sub(".*_", "", table$Variable) # Extract the suffix from the 'Variable' column

x <- c("SA", "VI", "CO", "DP", "AN") #Order in which suffixes should be arranged
suf_factor <- factor(suf, levels = x) # Convert suffixes to a factor with levels as defined in the custom order

table <- table[order(suf_factor, table$study), ] # Order the dataframe by the factor and study
rownames(table) <- NULL
```

## Headers and Subheaders

For Forester to visualize the data in a nice way we need to add headers containing the Names of the variables.
To do this we determine the first time a suffix appears and then interject a collumn containing the header before it.

First we create an empty row which we will use to fill in the text neccesary for the headers. 
```{r}
ER <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(ER) <- colnames(table) #adapt the structure of df table
```

Then we make two rows, one for Study 1 and one for Study 2 which we will later use as subheaders.
Here we also add an indication in the collumn "header" to allow us to mark this as a subgroup.
```{r}
G1 <- ER
G1$Variable <- "Study 1" #Add the header title, in this case indicating the study
G1$header <- 1

G2 <- ER
G2$Variable <- "Study 2" #Add the header title, in this case indicating the study
G2$header <- 1
```

### Self Actualization
We will then Subset each variable, add in the header (Full variable name), and the subheader (Study 1 or 2). To do this we determine the first appearance of the suffix, as well as the first time a 1 or 2 appear in the study collumn. We then add the row containing the Variable and Study. We do this for every variable.

```{r}

fsi <- function(df, column, suffix) { #function determining the first position of a suffix (not very usefull in this case as i solves this by subsetting, i left the code in as to not have to rewrite it and make it work on every piece of data here avoiding to just inject a row)
  matches <- grepl(suffix, df[[column]])
  which(matches)[1]
}


SA_S <- table[grepl("_SA$", table$Variable), ] #Subset all Self actualization variables

SA_H <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(SA_H) <- colnames(table) #adapt the structure of df table
SA_H$Variable <- "Self Actualization" #Add the header title, always the full name of the suffix

SA <- fsi(SA_S, "Variable", "_SA") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(SA)) { #Self Actualization (SA)
  SA_S <- rbind(SA_S[1:(SA) - 1, ], SA_H, SA_S[SA:nrow(SA_S), ]) # Insert the header before each new appearance of a suffix
}

SA_G1<- which(SA_S$study == 1)[1]
if (!is.na(SA_G1)) { #Add grouping variable
  SA_S <- rbind(SA_S[1:(SA_G1) - 1, ], G1, SA_S[SA_G1:nrow(SA_S), ]) # Insert the header before each new appearance of a suffix
}

SA_G2<- which(SA_S$study == 2)[1]
if (!is.na(SA_G2)) { #Add grouping variable
  SA_S <- rbind(SA_S[1:(SA_G2) - 1, ], G2, SA_S[SA_G2:nrow(SA_S), ]) # Insert the header before each new appearance of a suffix
}


```

### Vitality 
```{r}
VI_S <- table[grepl("_VI$", table$Variable), ] #Subset all Vitality variables

VI_H <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(VI_H) <- colnames(table) #adapt the structure of df table
VI_H$Variable <- "Vitality" #Add the header title, always the full name of the suffix

VI <- fsi(VI_S, "Variable", "_VI") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(VI)) { #Vitality (VI)
  VI_S <- rbind(VI_S[1:(VI) - 1, ], VI_H, VI_S[VI:nrow(VI_S), ]) # Insert the header before each new appearance of a suffix
}

VI_G1<- which(VI_S$study == 1)[1]
if (!is.na(VI_G1)) { #Add grouping variable
  VI_S <- rbind(VI_S[1:(VI_G1) - 1, ], G1, VI_S[VI_G1:nrow(VI_S), ]) # Insert the header before each new appearance of a suffix
}

VI_G2<- which(VI_S$study == 2)[1]
if (!is.na(VI_G2)) { #Add grouping variable
  VI_S <- rbind(VI_S[1:(VI_G2) - 1, ], G2, VI_S[VI_G2:nrow(VI_S), ]) # Insert the header before each new appearance of a suffix
}
```

### Control Orientation 
```{r}
CO_S <- table[grepl("_CO$", table$Variable), ] #Subset all Control Orientation variables

CO_H <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(CO_H) <- colnames(table) #adapt the structure of df table
CO_H$Variable <- "Control Orientation" #Add the header title, always the full name of the suffix

CO <- fsi(CO_S, "Variable", "_CO") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(CO)) { #COtality (CO)
  CO_S <- rbind(CO_S[1:(CO) - 1, ], CO_H, CO_S[CO:nrow(CO_S), ]) # Insert the header before each new appearance of a suffix
}

CO_G1<- which(CO_S$study == 1)[1]
if (!is.na(CO_G1)) { #Add grouping variable
  CO_S <- rbind(CO_S[1:(CO_G1) - 1, ], G1, CO_S[CO_G1:nrow(CO_S), ]) # Insert the header before each new appearance of a suffix
}

CO_G2<- which(CO_S$study == 2)[1]
if (!is.na(CO_G2)) { #Add grouping variable
  CO_S <- rbind(CO_S[1:(CO_G2) - 1, ], G2, CO_S[CO_G2:nrow(CO_S), ]) # Insert the header before each new appearance of a suffix
}
```

### Depression
```{r}
DP_S <- table[grepl("_DP$", table$Variable), ] #Subset all Depression variables

DP_H <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(DP_H) <- colnames(table) #adapt the structure of df table
DP_H$Variable <- "Depression" #Add the header title, always the full name of the suffix

DP <- fsi(DP_S, "Variable", "_DP") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(DP)) { #Depression (DP)
  DP_S <- rbind(DP_S[1:(DP) - 1, ], DP_H, DP_S[DP:nrow(DP_S), ]) # Insert the header before each new appearance of a suffix
}

DP_G1<- which(DP_S$study == 1)[1]
if (!is.na(DP_G1)) { #Add grouping variable
  DP_S <- rbind(DP_S[1:(DP_G1) - 1, ], G1, DP_S[DP_G1:nrow(DP_S), ]) # Insert the header before each new appearance of a suffix
}

DP_G2<- which(DP_S$study == 2)[1]
if (!is.na(DP_G2)) { #Add grouping variable
  DP_S <- rbind(DP_S[1:(DP_G2) - 1, ], G2, DP_S[DP_G2:nrow(DP_S), ]) # Insert the header before each new appearance of a suffix
}
```

### Anxiety
```{r}
AN_S <- table[grepl("_AN$", table$Variable), ] #Subset all Anxiety variables

AN_H <- data.frame(matrix(NA, ncol = ncol(table), nrow = 1)) #create an empty row
colnames(AN_H) <- colnames(table) #adapt the structure of df table
AN_H$Variable <- "Anxiety" #Add the header title, always the full name of the suffix

AN <- fsi(AN_S, "Variable", "_AN") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(AN)) { #Anxiety (AN)
  AN_S <- rbind(AN_S[1:(AN) - 1, ], AN_H, AN_S[AN:nrow(AN_S), ]) # Insert the header before each new appearance of a suffix
}

AN_G1<- which(AN_S$study == 1)[1]
if (!is.na(AN_G1)) { #Add grouping variable
  AN_S <- rbind(AN_S[1:(AN_G1) - 1, ], G1, AN_S[AN_G1:nrow(AN_S), ]) # Insert the header before each new appearance of a suffix
}

AN_G2<- which(AN_S$study == 2)[1]
if (!is.na(AN_G2)) { #Add grouping variable
  AN_S <- rbind(AN_S[1:(AN_G2) - 1, ], G2, AN_S[AN_G2:nrow(AN_S), ]) # Insert the header before each new appearance of a suffix
}
```

## Final preperations
Now that we have added all neccesarry information into the dataset we can now rbind them back into one dataframe
We then add indentations to the headers, and rename the variables to make it easier to read.

```{r}
table <- rbind(SA_S,VI_S,CO_S,DP_S,AN_S) #rbind subsetted dataframes back together


table$Variable <- ifelse(is.na(table$header), #add an indentation to variables containing an entry in the header collumn
                         table$Variable,
                         paste0("  ", table$Variable))

# Change the value in the Variable column based on multiple conditions
table$Variable <- ifelse(grepl("SAI_", table$Variable), "Self Accpetnace I",
                  ifelse(grepl("AFI_", table$Variable), "Affiliation I",
                  ifelse(grepl("CFI_", table$Variable), "Community Feeling I",
                  ifelse(grepl("SAC_", table$Variable), "Self Acceptance C",
                  ifelse(grepl("AFC_", table$Variable), "Affiliation C",
                  ifelse(grepl("CFC_", table$Variable), "Community Feeling C",
                  ifelse(grepl("FA", table$Variable), "Family",
                  ifelse(grepl("WE", table$Variable), "Global Welfare",
                    table$Variable))))))))

table$Variable <- ifelse(is.na(table$study), #add two indentation in each row containing a Study ID
                         table$Variable,
                         paste0("       ", table$Variable))

write.csv2(table,"./data/forester_data/cohens_d_forester.csv" )
```



# Correlation data preparation (Cohens D Cor)
As the original publication did not compute confidence intervalls for correlations we have to add them before we transform the data to make it compatible with forester, using the DescTools package.

```{r}
df2 <- as.data.frame(df2) #make sure df2 is a dataframe

for(i in 1:nrow(df2)){ #Create a conf intervall around the correlation and then rbind them together.
  x <- DescTools::CorCI(df2$correlation[i], df2$n[i], conf.level = 0.95, alternative=c("two.sided"))
  if(i == 1) {
    correlations_CI <- x
  } else {
    correlations_CI <- rbind(correlations_CI, x) # Add new data to dataframe
  }
}

correlations_CI <- as.data.frame(correlations_CI) #make sure correlations_CI is a dataframe

#Add back collumns nessecary for identification
correlations_CI$variable <- df2$variable
correlations_CI$study <- df2$study
correlations_CI$n <- df2$n

#write.csv2(correlations_CI, "./data/correlations_CI.csv")
```

##Load prepared correlation data
To avoid rerunning previous code
```{r}
table2 <- read.csv2("./data/correlations_CI.csv")
table2 <- table2%>%select(-1)
```

## Preparing data structure, analogous to T-Test data
We will start by preparing all data used in the plots as forester requires a certain data structure.
Here we will add the lines telling us which variable and study is used.

First we start by subsetting the dataset using only the neccesary collumns.
We then sort those by the Suffixes (Suffix = Variable) and study.

```{r}
#Subsetting data and renaming variables for easier datahandling
table2 <- table2%>%select(-c("n"))

table2 <- table2 %>%  #renaming variable
              rename(
                Variable = variable
 )

table2$header <- NA

# Sort data
suf <- sub(".*_", "", table2$Variable) # Extract the suffix from the 'Variable' column

x <- c("SA", "VI", "CO", "DP", "AN") #Order in which suffixes should be arranged
suf_factor <- factor(suf, levels = x) # Convert suffixes to a factor with levels as defined in the custom order

table2 <- table2[order(suf_factor, table2$study), ] # Order the dataframe by the factor and study
rownames(table) <- NULL
```

With the data sorted we can now add the Header and Subheaders.

## Headers and Subheaders
For Forester to visualize the data in a nice way we need to add headers containing the Names of the variables.
To do this we determine the first time a suffix appears and then interject a collumn containing the header before it.

First we create an empty row which we will use to fill in the text neccesary for the headers. 
```{r}
ER2 <- data.frame(matrix(NA, ncol = ncol(table2), nrow = 1)) #create an empty row
colnames(ER2) <- colnames(table2) #adapt the structure of df table
```

Then we make two rows, one for Study 1 and one for Study 2 which we will later use as subheaders.
Here we also add an indication in the collumn "header" to allow us to mark this as a subgroup.

```{r}
G1_2 <- ER2
G1_2$Variable <- "Study 1" #Add the header title, in this case indicating the study
G1_2$header <- 1

G2_2 <- ER2
G2_2$Variable <- "Study 2" #Add the header title, in this case indicating the study
G2_2$header <- 1
```

### Self Actualization
We will then Subset each variable, add in the header (Full variable name), and the subheader (Study 1 or 2). To do this we determine the first appearance of the suffix, as well as the first time a 1 or 2 appear in the study collumn. We then add the row containing the Variable and Study. We do this for every variable.

```{r}
SA_S2 <- table2[grepl("_SA$", table2$Variable), ] #Subset all Self actualization variables

SA_H2 <- data.frame(matrix(NA, ncol = ncol(table2), nrow = 1)) #create an empty row
colnames(SA_H2) <- colnames(table2) #adapt the structure of df table
SA_H2$Variable <- "Self Actualization" #Add the header title, always the full name of the suffix

SA2 <- fsi(SA_S2, "Variable", "_SA") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(SA2)) { #Self Actualization (SA)
  SA_S2 <- rbind(SA_S2[1:(SA2) - 1, ], SA_H2, SA_S2[SA2:nrow(SA_S2), ]) # Insert the header before each new appearance of a suffix
}

SA_G1_2<- which(SA_S2$study == 1)[1]
if (!is.na(SA_G1_2)) { #Add grouping variable
  SA_S2 <- rbind(SA_S2[1:(SA_G1_2) - 1, ], G1_2, SA_S2[SA_G1_2:nrow(SA_S2), ]) # Insert the header before each new appearance of a suffix
}

SA_G2_2<- which(SA_S2$study == 2)[1]
if (!is.na(SA_G2_2)) { #Add grouping variable
  SA_S2 <- rbind(SA_S2[1:(SA_G2_2) - 1, ], G2_2, SA_S2[SA_G2_2:nrow(SA_S2), ]) # Insert the header before each new appearance of a suffix
}
```

### Vitality
```{r}
VI_S2 <- table2[grepl("_VI$", table2$Variable), ] #Subset all Vitality variables

VI_H2 <- data.frame(matrix(NA, ncol = ncol(table2), nrow = 1)) #create an empty row
colnames(VI_H2) <- colnames(table2) #adapt the structure of df table
VI_H2$Variable <- "Vitality" #Add the header title, always the full name of the suffix

VI2 <- fsi(VI_S2, "Variable", "_VI") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(VI2)) { #Vitality (VI)
  VI_S2 <- rbind(VI_S2[1:(VI2) - 1, ], VI_H2, VI_S2[VI2:nrow(VI_S2), ]) # Insert the header before each new appearance of a suffix
}

VI_G1_2<- which(VI_S2$study == 1)[1]
if (!is.na(VI_G1_2)) { #Add grouping variable
  VI_S2 <- rbind(VI_S2[1:(VI_G1_2) - 1, ], G1_2, VI_S2[VI_G1_2:nrow(VI_S2), ]) # Insert the header before each new appearance of a suffix
}

VI_G2_2<- which(VI_S2$study == 2)[1]
if (!is.na(VI_G2_2)) { #Add grouping variable
  VI_S2 <- rbind(VI_S2[1:(VI_G2_2) - 1, ], G2_2, VI_S2[VI_G2_2:nrow(VI_S2), ]) # Insert the header before each new appearance of a suffix
}
```

### Depression
```{r}
DP_S2 <- table2[grepl("_DP$", table2$Variable), ] #Subset all Depression variables

DP_H2 <- data.frame(matrix(NA, ncol = ncol(table2), nrow = 1)) #create an empty row
colnames(DP_H2) <- colnames(table2) #adapt the structure of df table
DP_H2$Variable <- "Depression" #Add the header title, always the full name of the suffix

DP2 <- fsi(DP_S2, "Variable", "_DP") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(DP2)) { #Depression (DP)
  DP_S2 <- rbind(DP_S2[1:(DP2) - 1, ], DP_H2, DP_S2[DP2:nrow(DP_S2), ]) # Insert the header before each new appearance of a suffix
}

DP_G1_2<- which(DP_S2$study == 1)[1]
if (!is.na(DP_G1_2)) { #Add grouping variable
  DP_S2 <- rbind(DP_S2[1:(DP_G1_2) - 1, ], G1_2, DP_S2[DP_G1_2:nrow(DP_S2), ]) # Insert the header before each new appearance of a suffix
}

DP_G2_2<- which(DP_S2$study == 2)[1]
if (!is.na(DP_G2_2)) { #Add grouping variable
  DP_S2 <- rbind(DP_S2[1:(DP_G2_2) - 1, ], G2_2, DP_S2[DP_G2_2:nrow(DP_S2), ]) # Insert the header before each new appearance of a suffix
}
```

### Anxiety
```{r}
AN_S2 <- table2[grepl("_AN$", table2$Variable), ] #Subset all Anxiety variables

AN_H2 <- data.frame(matrix(NA, ncol = ncol(table2), nrow = 1)) #create an empty row
colnames(AN_H2) <- colnames(table2) #adapt the structure of df table
AN_H2$Variable <- "Anxiety" #Add the header title, always the full name of the suffix

AN2 <- fsi(AN_S2, "Variable", "_AN") # Determine the position of the first time a variable/suffix appears in the dataset
if (!is.na(AN2)) { #Anxiety (AN)
  AN_S2 <- rbind(AN_S2[1:(AN2) - 1, ], AN_H2, AN_S2[AN2:nrow(AN_S2), ]) # Insert the header before each new appearance of a suffix
}

AN_G1_2<- which(AN_S2$study == 1)[1]
if (!is.na(AN_G1_2)) { #Add grouping variable
  AN_S2 <- rbind(AN_S2[1:(AN_G1_2) - 1, ], G1_2, AN_S2[AN_G1_2:nrow(AN_S2), ]) # Insert the header before each new appearance of a suffix
}

AN_G2_2<- which(AN_S2$study == 2)[1]
if (!is.na(AN_G2_2)) { #Add grouping variable
  AN_S2 <- rbind(AN_S2[1:(AN_G2_2) - 1, ], G2_2, AN_S2[AN_G2_2:nrow(AN_S2), ]) # Insert the header before each new appearance of a suffix
}
```

## Final preperations
Now that we have added all neccesarry information into the dataset we can now rbind them back into one dataframe
We then add indentations to the headers, and rename the variables to make it easier to read.

```{r}
table2 <- rbind(SA_S2,VI_S2,DP_S2, AN_S2) #rbind subsetted dataframes back together


table2$Variable <- ifelse(is.na(table2$header), #add an indentation to variables containing an entry in the header collumn
                         table2$Variable,
                         paste0("  ", table2$Variable))

# Change the value in the Variable column based on multiple conditions
table2$Variable <- ifelse(grepl("SAI_", table2$Variable), "Self Accpetnace I",
                  ifelse(grepl("AFI_", table2$Variable), "Affiliation I",
                  ifelse(grepl("CFI_", table2$Variable), "Community Feeling I",
                  ifelse(grepl("SAC_", table2$Variable), "Self Acceptance C",
                  ifelse(grepl("AFC_", table2$Variable), "Affiliation C",
                  ifelse(grepl("CFC_", table2$Variable), "Community Feeling C",
                  ifelse(grepl("FSI_", table2$Variable), "Financial Success I",
                  ifelse(grepl("FSC_", table2$Variable), "Financial Success C",
                    table2$Variable))))))))

table2$Variable <- ifelse(is.na(table2$study), #add two indentation in each row containing a Study ID
                         table2$Variable,
                         paste0("       ", table2$Variable))

write.csv2(table2,"./data/forester_data/correlations_CI_forester.csv" )
```

# Creating the Plots

##Reload Data to avoid running full script
```{r}
table <- read.csv2("./data/forester_data/cohens_d_forester.csv") #reload only dataset, avoids to repeat previous steps
table <- table %>% select(-1) #remove x collumn

table2 <- read.csv2("./data/forester_data/correlations_CI_forester.csv") #reload only dataset, avoids to repeat previous steps
table2 <- table2 %>% select(-1) #remove x collumn
```

## Forest Plot for Cohens_D
Using the forester Function we not print a forest plot using our previously prepared data.
```{r}

table_data <- data.frame(Variable = table$Variable) #extract the header data

forester(left_side_data = table_data,
         estimate = table$Estimate,
         ci_low = table$ci.lo,
         ci_high = table$ci.hi,
         display = FALSE,
         xlim = c(-1.5, 1.5),
         estimate_col_name = "D (95% CI)",
         estimate_precision = 3,
         stripe_colour = "#d3d3d3",
         file_path = here::here("plots/Cohens_D_Plots_CR1993.png"))
#         font_family = "Fira Sans") # Comment this if your using a mac or did not install the alternative font
```

## Forest Plot for correlations
Using the forester Function we not print a forest plot using our previously prepared data.
```{r}

table_data2 <- data.frame(Variable = table2$Variable)

forester(left_side_data = table_data2,
         estimate = table2$cor,
         ci_low = table2$lwr.ci,
         ci_high = table2$upr.ci,
         display = FALSE,
         xlim = c(-1, 1),
         estimate_col_name = "COR (95% CI)",
         estimate_precision = 3,
         stripe_colour = "#d3d3d3",
         file_path = here::here("plots/Correlations_CI_Plots_CR1993.png"))
```
