---
title: "Power Analysis"
author: "Dominik Meindl"
date: "2023-11-27"
output: html_document
---

# Packages
```{r}
#Packages---- using R4.3.2

library(pwr) #1.3-0
library(esc) #0.5.1
library(readr) #2.1.4
library(tidyverse) #2.0.0
```

#Load Data
This is raw data extracted from the publication. Such as Means, standard deviations, t values and significance (.05 or .10) as well as which study this data has been extracted from.

df = all values concerning t tests
- mx: mean of first variable
- my: mean of second variable (FSI/FSC)
- sdx: sd of first variable
- sdy: sd of second variable (FSI/FSC)
- t: t-value
- sig05: 1 if p <.05
- sig10: 1 if p <.10
- study: 1 for study 1, 2 for study 2
- n: sample size

df2 = all values concerning correlations
- beta: beta values
- correlation: Pearsons r
- sig05_beta: 1 if p <.05 (beta)
- sig05_cor: 1 if p <.05 (r)
- sig10_beta: 1 if p <.10 (beta)
- sig10_cor: 1 if p <.10 (r)
- study: 1 for study 1, 2 for study 2
- n: sample size

```{r Data Loading, message=FALSE}
#load data----
df <- read_csv2("./data/ttests_raw.csv")
df2 <- read_csv2("./data/correlations_raw.csv")
```

## Power Transformations - Cohens D Values of T-Tests
Calculate Cohens d for all t-tests using a custom function.
We will then remerge this date with the original dataframe to get one file containing all information. 
This is the same code as used in Power_Analysis.rmd.

Due to an error introduced by R 4.3.2 we had to change our approach, we now have to use custom code to extract the same data as the esc::esc_mean_sd function.

```{r}
# custom Function to calculate Cohen's d and its statistics
cohen_d_with_stats <- function(mx, my, sdx, sdy, n) {
  pooled_sd <- sqrt(((n - 1) * sdx^2 + (n - 1) * sdy^2) / (n + n - 2))
  d <- (mx - my) / pooled_sd
  var_d <- (n + n) / (n * n) + (d^2 / (2 * (n + n - 2)))
  se_d <- sqrt(var_d)
  ci_95_low <- d - 1.96 * se_d
  ci_95_high <- d + 1.96 * se_d
  return(c(d, var_d, se_d, ci_95_low, ci_95_high))
}

# Apply the function to each row
results <- apply(df, 1, function(x) cohen_d_with_stats(as.numeric(x['mx']), 
                                                       as.numeric(x['my']), 
                                                       as.numeric(x['sdx']), 
                                                       as.numeric(x['sdy']), 
                                                       as.numeric(x['n'])))

# Converting results to a dataframe
results_df <- as.data.frame(t(results))
names(results_df) <- c("es", "var", "se", "ci.lo", "ci.hi")

# Merging results with the original dataframe
cohens_d <- cbind(df, results_df)

#write.csv2(cohens_d, "./data/cohens_d_ttests.csv")
```

#Power Transformations - Cohens D Values of correlations
```{r}
#cohens d calc. for correlations ----
cohens_d_r <- esc::cohens_d(df2$correlation) #as there is no SD given for the variables (check with LEO to see if im not misinterpreting something here)
cohens_d_r <- as.data.frame(cohens_d_r)

cohens_d_r$variable <- df2$variable
cohens_d_r$study <- df2$study

#write_csv2(cohens_d_r, "./data/cohens_d_corr.csv") 
```

## Power Tests for t-tests and correlations.
Power calculations for the study have been conducted by adjusting multiple criteria.

An effect size of 0.3 has been chosen as this was the smallest (as significant) reported effect. 
Alpha has been Bonffroni corrected, to be 0.0009090909 (0.05/55, 55 as the amount of seperate t tests conducted).
We also adjusted the power level to 0.99. #So argumentieren oder anders?

For the correlations we used r=.21 as the smallest effect size of interest. 

```{r}
#PWR Calc for n ----
pwr.t.test(d=0.3, sig.level = 0.0009090909, power=0.99, type="two.sample", )

pwr.r.test(r=0.21, power=0.99, alternative = "two.sided")
```

For the t-tests we found a sample size of n≈711 per group. Therefore we need a sample of n=1422 for the study to be sufficiently powered.

For the correlations we found a sample size needed of n≈407 participants per group. We therefore need a sample of n=814 for it to be suffiziently powered.

We decided for the sample size of n=1422 as this is those are the more important measures, going with 1422 also allows us to have both measures sufficiently powered for later analysis.
