---
title: "Power Analysis"
author: "Dominik Meindl"
date: "2023-11-27"
output: html_document
---

# Packages
```{r}
#Packages----
library(pwr)
library(esc)
library(readr)
```

#Load Data
This is raw data extracted from the publication. Such as Means, standard deviations, t values and significance (.05 or .10) as well as which study this data has been extracted from.

df = all values concerning t tests
df2 = all values concerning correlations

```{r}
#load data----
df <- read_csv2("./data/ttests_raw.csv")
df2 <- read_csv2("./data/correlations_raw.csv")
```

#Power Transformations - Cohens D Values of T-Tests
Calculate Cohens d for all t-tests using the esc package.
Afterwards we will add the variable descriptions as well as the Study ID to the dataframe. 

```{r}
#cohens d calc. for t tests-----
cohens_d <- esc::esc_mean_sd( grp1n=df$n, grp1m=df$mx, grp1sd = df$sdx, grp2n = df$n, grp2m = df$my, grp2sd = df$sdy, es.type="d")
cohens_d <- as.data.frame(cohens_d)

cohens_d$variable <- df$variable
cohens_d$study <- df$study

cohens_d_r <- esc::cohens_d(df2$correlation) #as there is no SD given for the variables (check with LEO to see if im not misinterpreting something here)
cohens_d_r <- as.data.frame(cohens_d_r)
cohens_d_r$variable <- df2$variable
cohens_d_r$study <- df2$study

#write.csv2(cohens_d, "./data/cohens_d_ttests.csv") 
```

## Power Tests for t-tests and correlations.
Power calculations for the study have been conducted by adjusting multiple criteria.

An effect size of 0.3 has been chosen as this was the smallest (as significant) reported effect. 
Alpha has been Bonffroni corrected, to be 0.0009090909 (0.05/55, 55 as the amount of seperate t tests conducted).
We also adjusted the power level to 0.99. #So argumentieren oder anders?

For the correlations we used r=.21 as the smallest effect size of interest. 

```{r}
#PWR Calc for n ----
pwr.t.test(d=0.3, sig.level = 0.0009090909, power=0.99, type="two.sample", )

pwr.r.test(r=0.21, power=0.99, alternative = "two.sided")
```

For the t-tests we found a sample size of n≈711 per group. Therefore we need a sample of n=1422 for the study to be sufficiently powered.

For the correlations we found a sample size needed of n≈407 participants per group. We therefore need a sample of n=814 for it to be suffiziently powered.

We decided for the sample size of n=1422 as this is those are the more important measures, going with 1422 also allows us to have both measures sufficiently powered for later analysis.
